Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-07 Paper.tex
Cleanups and additional text.

\documentclass[9pt,oneside]{amsart}
%\usepackage{tweaklist}
\usepackage{url}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}

@@

Incorruptability of judgement. Transparency. Open state. User can be guaranteed that backend will do what front-end says it will. Parties can analyse and be wholly confident in outcomes given events.

\subsection{Previous Work} \label{ch:previous}

E language. Smart contracts. Bitcoin, namecoin \&c. Mastercoin.

@@

We can assert its validity if and only if it satisfies several conditions: It must be internally consistent with the uncle and transaction block hashes; the given transactions $\mathbf{T}$, when executed in order on the base state $\mathbb{S}$ result in a new state of the identity $H_r$:
\begin{eqnarray}
& & \mathcal{S}(\mathcal{R}(\mathbf{U})) \equiv H_u \\
& \wedge & \mathcal{S}(\mathcal{R}(\mathbf{T})) \equiv H_t \\
& \wedge & r(\Pi(\mathbb{S}, B)) \equiv H_r
\end{eqnarray}

@@

We define $P(B_H)$ to be the parent block of $B$, formally:
\begin{equation}
P(H) \equiv B': \mathcal{S}(\mathcal{R}(B')) = H_p
\end{equation}

@@

The nonce, $H_n$, must satisfy the relation:
\begin{equation}
\mathcal{P}(H, H_n) \leqslant \frac{2^{256}}{H_d}
\end{equation}

Where $\mathcal{P}$ is the proof-of-work function (see section \ref{ch:pow}): this evaluates to an pseudo-random number cryptographically dependent on the parameters $H$ and $H_n$. Given an approximately uniform distribution in the range $[0, 2^{256})$, the expected time to find a solution is proportional to the difficulty, $H_d$.

@@

Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv & \mathcal{P}(H, H_n) \leqslant \frac{2^{256}}{H_d} \\
& \wedge & H_d = D(H) \\
& \wedge & H_t > {P(H)_H}_t
\end{eqnarray}

@@

The address of the new contract is defined as being the rightmost 160 bits of the SHA3 hash of RLP encoding of the structure \texttt{[ sender, nonce ]}. In the unlikely event that the address is already in use, it is treated as a big-endian integer and incremented by one until an unused address is arrived at. Thus we define the creation address function $A$:
\begin{eqnarray}
A(s, n) & \equiv & a \quad \text{where:} \\
a & = & \arg \min_x : x \geqslant a' \wedge \mathbb{S}_0[x] = \varnothing \\
a' & = & \mathcal{B}_{96..255}(\mathcal{S}(\mathcal{R}([s, n])))
\end{eqnarray}

where $\mathcal{S}$ is the SHA3 256-bit hash function, $\mathcal{R}$ is the RLP encoding function, $\mathcal{B}_{a..b}(X)$ evaluates to binary value containing the bits of indices in the range $[a, b]$ of the binary data $X$ and $\mathbb{S}_0[x]$ is the address state of $x$ or $\varnothing$ if none exists. Note we use one fewer than the sender's nonce value; we assert that we have incremented the sender account's nonce prior to this call, and so the value used is the sender's nonce at the beginning of the responsible transaction or VM operation.

The account's nonce is initially defined as zero, the balance as the value passed, the storage as empty and the code hash as the SHA3 256-bit hash of the code, thus the mutated state becomes $\mathbb{S}^*$:
\begin{eqnarray}
\mathbb{S}^* & \equiv & \mathbb{S} \quad \text{except:} \\
\mathbb{S}^*[A(s, \mathbb{S}[s]_{nonce})] & \equiv & ( 0, v, \varnothing, \mathcal{S}(\mathbf{b}) )
\end{eqnarray}

It is asserted that the state database will also change such that it defines the pair $(\mathcal{S}(\mathbf{b}), \mathbf{b})$.

@@

If the recipient account contains no code to be executed (i.e. it's not a contract), then we define the final state as being equivalent to the rollback state. In the case that the recipient contains code to be executed (i.e. that the account is a contract), then the contract's body code (identified as the fragment whose SHA3 hash is $\mathbb{S}[r]_{code}]$) is executed according to the execution model (see section \ref{ch:model}). Just as with contract creation, if the execution halts due to an exhausted gas supply, then no gas is refunded to the caller and the state is reverted to the point immediately prior to code execution.
\begin{eqnarray}
\mathbb{S}' & \equiv & \begin{cases}
\mathbb{S}_1 & \text{if} \quad \mathbb{S}_1[r]_{code} = \varnothing \\
\mathbb{S}_1 & \text{if} \quad \mathbb{S}^{**} = \varnothing \\
\mathbb{S}^{**} & \text{otherwise}
\end{cases} \\
(\mathbb{S}^{**}, g', \mathbf{o}) & \equiv & \Xi(\mathbb{S}_1, g, I) \\
I_a & \equiv & a \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & \mathbf{d} \\
I_s & \equiv & s \\
I_v & \equiv & v \\
\text{Let} \quad \mathcal{S}(I_\mathbf{b}) & = & \mathbb{S}[r]_{code}
\end{eqnarray}

We assert that the state database contains the entry $(\mathcal{S}(I_\mathbf{b}), I_\mathbf{b})$.

@@

Thus we define the total difficulty of block $B$ recursively as:
\begin{eqnarray}
B_t & \equiv & B'_t + B_d + \sum\limits_{U \in B_\mathbf{U}} U_d \\
B' & \equiv & P(H) \\
H & \equiv & B_H \\
\end{eqnarray}

@@

\subsubsection{Uncle Validation}

@@

\subsubsection{Reward Application}

@@

\subsubsection{State \& Nonce Validation}

@@

And finally define $\Phi$, the block transition function, which maps an incomplete block $B$ to a complete block $B'$:
\begin{eqnarray}
\Phi(B) & \equiv & B': \quad B' = B^* \quad \text{except:} \\
B'_n & = & n: \quad \mathcal{P}(B^*, n) < \frac{2^{256}}{H_d} \\
B^* & \equiv & B \quad \text{except:} \quad B'_r = r(\Pi(\Gamma(B), B))
\end{eqnarray}

@@

Thus the complete block-transition mechanism, less $\mathcal{P}$, the proof-of-work function is defined.

@@

More formally, the proof-of-work function takes the form of $\mathcal{P}$:

\begin{equation}
\mathcal{P}(H, n) < \frac{2^{256}}{H_d}
\end{equation}

Where $H$ is the new block's header \textit{without} the nonce entry; $H_d$ is the difficulty value (i.e. the block difficulty from section \ref{ch:ghost}).

@@

It is formally defined as $\mathcal{P}$:
\begin{equation}
\mathcal{P}(H, n) \equiv \mathcal{B}(\mathcal{S}(\mathcal{S}(\mathcal{R}(H)) \circ n))
\end{equation}

where:
$\mathcal{R}(H)$ is the RLP encoding of the $H$;
$\mathcal{S}$ is the SHA3 hash function accepting an arbitrary length series of bytes and evaluating to a series of 32 bytes (i.e. 256-bit);
$n$ is the nonce, a series of 32 bytes;
$\circ$ is the series concatenation operator;
$\mathcal{B}(X)$ evaluates to the value equal to X when interpreted as a big-endian-encoded integer.

@@

Rether than being hard-specified in the protocol, the block limit will become based upon some fixed ratio about a long-term moving average of actual gas usage in blocks, allowing it to slowly increase according to the network's ability to manage the transaction volume.

@@

Throw out nodes in state that haven't sent/received a transaction in over X blocks.

@@

\section{Recursive Length Prefix}\label{app:rlp}

This is a method for encoding arbitrarily structured binary data (byte arrays).

\section{Modified Merkle Patricia Tree}\label{app:trie}

The modified Merkle Patricia tree (trie) provides a persistent data structure to map between arbitrary-length binary data (byte arrays). It is defined in terms of a mutable data structure to map between 256-bit binary fragments and arbitrary-length binary data, typically implemented as a database.

\section{Hex-Prefix Encoding}\label{app:hexprefix}

Hex-prefix encoding is an efficient method of encoding a arbitrary number of nibbles as a byte array. It is able to store an additional flag which, when used in the context of the trie (the only context in which it is used), disambiguates between node types.

\section{Formal Specification of Structures}

Though RLP is data-agnostic, it does specify a canonical representation for integer quantities. It is big-endian with no leading zero-bytes. Thus for elements than feasibly can be stored as integers, it becomes important to specify whether they should adhere to this canonical representation or be left in some other (perhaps more 'native') format.

@@

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{20s: SHA3}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x20 & {\small SHA3} & 2 & 1 & Compute SHA3-256 hash. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathcal{S}(\mathbb{M}_M[ \mathbb{M}_S[0] \dots (\mathbb{M}_S[0] + \mathbb{M}_S[1] - 1) ])$ \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ (\mathbb{M}_S[0] + \mathbb{M}_S[1]) \div 32 })$ \\
\bottomrule
\end{tabular*}

@@

\section{Low-level Lisp-like Language}\label{app:lll}

The Low-level Lisp-like Language is a language created in order to efficiently author low-level programs (contracts) without having to resort to EVM-Assembly.

\section{Wire Protocol}\label{app:wire}

The wire-protocol specifies a network-level protocol for how two peers can communicate. It includes handshake procedures and the means for transfering information such as blocks \& transactions

\section{Peer Strategy}\label{app:peers}

@@

$\langle 0_{256}, \mathcal{S}(\mathcal{R}([])), 0_{160}, 0_{256}, \mathcal{S}(\mathcal{R}([])), 2^{22}, 0, [], 42 \rangle$

@@

$\mathcal{S}(\mathcal{R}([]))$ values refer to the hashes of the transaction and uncle lists in RLP, both empty.

>>>>

\documentclass[9pt,oneside]{amsart}
%\usepackage{tweaklist}
\usepackage{url}
\usepackage{cancel}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}

\newcommand{\hcancel}[1]{%
    \tikz[baseline=(tocancel.base)]{
        \node[inner sep=0pt,outer sep=0pt] (tocancel) {#1};
        \draw[black] (tocancel.south west) -- (tocancel.north east);
    }%
}%

@@

There are many goals of this project; one key goal is to facilitate transactions between consenting individuals who would otherwise have no means to trust one another. This may be due to geographical separation, interfacing difficulty, or perhaps the incompatibility, incompetance, unwillingness, expense, uncertainty, inconvenience or corruption of existing legal systems. By specifying a state-change system through a rich and unambiguous language, and furthermore architecting a system such that we can reasonably expect that an agreement will be thus enforced autonomously, we can provide a means to this end.

Dealings in this proposed system would have several attributes not often found in the real word. The incorruptibility of judgement, often difficult to find, comes naturally from a disinterested algorithmic interpreter. Transparency, through being about to see exactly how a state or judgement came about through the transaction log and rules or instructional codes never happens perfectly in human-based systems.

Overall, we wish to provide a system such that the user can be guaranteed that any other individuals, systems or organisations that they interact with, they can do so with absolute confidence in the possible outcomes and how they might come about.

%\subsection{Previous Work} \label{ch:previous}
%E language. Smart contracts. Bitcoin, namecoin \&c. Mastercoin.

@@

We can assert its validity if and only if it satisfies several conditions: It must be internally consistent with the uncle and transaction block hashes; the given transactions $\mathbf{T}$, when executed in order on the base state $\mathbb{S}$ result in a new state of the identity $H_r$:
\begin{eqnarray}
& & \mathtt{\tiny SHA3}(\mathtt{\tiny RLP}(\mathbf{U})) \equiv H_u \\
& \wedge & \mathtt{\tiny SHA3}(\mathtt{\tiny RLP}(\mathbf{T})) \equiv H_t \\
& \wedge & r(\Pi(\mathbb{S}, B)) \equiv H_r
\end{eqnarray}

@@

We define $P(B_H)$ to be the parent block of $B$, formally:
\begin{equation}
P(H) \equiv B': \mathtt{\tiny SHA3}(\mathtt{\tiny RLP}(B')) = H_p
\end{equation}

@@

The nonce, $H_n$, must satisfy the relation:
\begin{equation}
\mathtt{PoW}(H, H_n) \leqslant \frac{2^{256}}{H_d}
\end{equation}

Where $\mathtt{PoW}$ is the proof-of-work function (see section \ref{ch:pow}): this evaluates to an pseudo-random number cryptographically dependent on the parameters $H$ and $H_n$. Given an approximately uniform distribution in the range $[0, 2^{256})$, the expected time to find a solution is proportional to the difficulty, $H_d$.

@@

Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv & \mathtt{PoW}(H, H_n) \leqslant \frac{2^{256}}{H_d} \\
& \wedge & H_d = D(H) \\
& \wedge & H_t > {P(H)_H}_t
\end{eqnarray}

@@

The address of the new contract is defined as being the rightmost 160 bits of the SHA3 hash of RLP encoding of the structure \texttt{[ sender, nonce ]}. In the unlikely event that the address is already in use, it is treated as a big-endian integer and incremented by one until an unused address is arrived at. Thus we define the creation address function $A$:
\begin{eqnarray}
A(s, n) & \equiv & a \quad \text{where:} \\
a & = & \arg \min_x : x \geqslant a' \wedge \mathbb{S}_0[x] = \varnothing \\
a' & = & \mathcal{B}_{96..255}\Big(\mathtt{\tiny SHA3}\Big(\mathtt{\tiny RLP}\big(\;\langle s, n\rangle\;\big)\Big)\Big)
\end{eqnarray}

where $\mathtt{\tiny SHA3}$ is the SHA3 256-bit hash function, $\mathtt{\tiny RLP}$ is the RLP encoding function, $\mathcal{B}_{a..b}(X)$ evaluates to binary value containing the bits of indices in the range $[a, b]$ of the binary data $X$ and $\mathbb{S}_0[x]$ is the address state of $x$ or $\varnothing$ if none exists. Note we use one fewer than the sender's nonce value; we assert that we have incremented the sender account's nonce prior to this call, and so the value used is the sender's nonce at the beginning of the responsible transaction or VM operation.

The account's nonce is initially defined as zero, the balance as the value passed, the storage as empty and the code hash as the SHA3 256-bit hash of the code, thus the mutated state becomes $\mathbb{S}^*$:
\begin{eqnarray}
\mathbb{S}^* & \equiv & \mathbb{S} \quad \text{except:} \\
\mathbb{S}^*[A(s, \mathbb{S}[s]_{nonce})] & \equiv & ( 0, v, \varnothing, \mathtt{\tiny SHA3}(\mathbf{b}) )
\end{eqnarray}

It is asserted that the state database will also change such that it defines the pair $(\mathtt{\tiny SHA3}(\mathbf{b}), \mathbf{b})$.

@@

If the recipient account contains no code to be executed (i.e. it's not a contract), then we define the final state as being equivalent to the rollback state. In the case that the recipient contains code to be executed (i.e. that the account is a contract), then the contract's body code (identified as the fragment whose SHA3 hash is $\mathbb{S}[r]_{code}]$) is executed according to the execution model (see section \ref{ch:model}). Just as with contract creation, if the execution halts due to an exhausted gas supply, then no gas is refunded to the caller and the state is reverted to the point immediately prior to code execution.
\begin{eqnarray}
\mathbb{S}' & \equiv & \begin{cases}
\mathbb{S}_1 & \text{if} \quad \mathbb{S}_1[r]_{code} = \varnothing \\
\mathbb{S}_1 & \text{if} \quad \mathbb{S}^{**} = \varnothing \\
\mathbb{S}^{**} & \text{otherwise}
\end{cases} \\
(\mathbb{S}^{**}, g', \mathbf{o}) & \equiv & \Xi(\mathbb{S}_1, g, I) \\
I_a & \equiv & a \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & \mathbf{d} \\
I_s & \equiv & s \\
I_v & \equiv & v \\
\text{Let} \quad \mathtt{\tiny SHA3}(I_\mathbf{b}) & = & \mathbb{S}[r]_{code}
\end{eqnarray}

We assert that the state database contains the entry $(\mathtt{\tiny SHA3}(I_\mathbf{b}), I_\mathbf{b})$.

@@

Thus we define the total difficulty of block $B$ recursively as:
\begin{eqnarray}
B_t & \equiv & B'_t + B_d + \sum\limits_{U \in B_\mathbf{U}} U_d \\
B' & \equiv & P(H) \\
H & \equiv & B_H
\end{eqnarray}

@@

\subsection{Uncle Validation}

@@

\subsection{Reward Application}

@@

\subsection{State \& Nonce Validation}

@@

And finally define $\Phi$, the block transition function, which maps an incomplete block $B$ to a complete block $B'$:
\begin{eqnarray}
\Phi(B) & \equiv & B': \quad B' = B^* \quad \text{except:} \\
B'_n & = & n: \quad \mathtt{PoW}(B^*, n) < \frac{2^{256}}{H_d} \\
B^* & \equiv & B \quad \text{except:} \quad B'_r = r(\Pi(\Gamma(B), B))
\end{eqnarray}

@@

Thus the complete block-transition mechanism, less $\mathtt{PoW}$, the proof-of-work function is defined.

@@

More formally, the proof-of-work function takes the form of $\mathtt{PoW}$:
\begin{equation}
\mathtt{PoW}(H_{\hcancel{n}}, n) < \frac{2^{256}}{H_d}
\end{equation}

Where $H_{\hcancel{n}}$ is the new block's header $H$, but \textit{without} the nonce component; $H_d$ is the new block's difficulty value (i.e. the block difficulty from section \ref{ch:ghost}).

@@

It is formally defined as $\mathtt{PoW}$:
\begin{equation}
\mathtt{PoW}(H, n) \equiv \mathtt{BE}(\mathtt{\tiny SHA3}(\mathtt{\tiny SHA3}(\mathtt{\tiny RLP}(H_{\hcancel{n}})) \circ n))
\end{equation}

where:
$\mathtt{\tiny RLP}(H_{\hcancel{n}})$ is the RLP encoding of the block header $H$, not including the final nonce component;
$\mathtt{\tiny SHA3}$ is the SHA3 hash function accepting an arbitrary length series of bytes and evaluating to a series of 32 bytes (i.e. 256-bit);
$n$ is the nonce, a series of 32 bytes;
$\circ$ is the series concatenation operator;
$\mathtt{BE}(X)$ evaluates to the value equal to X when interpreted as a big-endian-encoded integer.

@@

Rather than being hard-specified in the protocol, the block limit will become based upon some fixed ratio about a long-term moving average of actual gas usage in blocks, allowing it to slowly increase according to the network's ability to manage the transaction volume.

@@

Nodes in state trie that haven't sent/received a transaction in over X blocks could be thrown out, reducing Ether-leakage and reducing the growth of the state database.

@@

\section{Recursive Length Prefix}\label{app:rlp}
This is a method for encoding arbitrarily structured binary data (byte arrays).

\section{Modified Merkle Patricia Tree}\label{app:trie}
The modified Merkle Patricia tree (trie) provides a persistent data structure to map between arbitrary-length binary data (byte arrays). It is defined in terms of a mutable data structure to map between 256-bit binary fragments and arbitrary-length binary data, typically implemented as a database.

\section{Hex-Prefix Encoding}\label{app:hexprefix}
Hex-prefix encoding is an efficient method of encoding a arbitrary number of nibbles as a byte array. It is able to store an additional flag which, when used in the context of the trie (the only context in which it is used), disambiguates between node types.

\section{Formal Specification of Structures}
Though RLP is data-agnostic, it does specify a canonical representation for integer quantities. It is big-endian with no leading zero-bytes. Thus for elements than feasibly can be stored as integers, it becomes important to specify whether they should adhere to this canonical representation or be left in some other (perhaps more 'native') format.

@@

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{20s: SHA3}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x20 & {\small SHA3} & 2 & 1 & Compute SHA3-256 hash. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathtt{\tiny SHA3}(\mathbb{M}_M[ \mathbb{M}_S[0] \dots (\mathbb{M}_S[0] + \mathbb{M}_S[1] - 1) ])$ \\
&&&& $\mathbb{M}'_i \equiv \max(\mathbb{M}_i, \ceil{ (\mathbb{M}_S[0] + \mathbb{M}_S[1]) \div 32 })$ \\
\bottomrule
\end{tabular*}

@@

%\section{Low-level Lisp-like Language}\label{app:lll}
%The Low-level Lisp-like Language is a language created in order to efficiently author low-level programs (contracts) without having to resort to EVM-Assembly.

\section{Wire Protocol}\label{app:wire}
The wire-protocol specifies a network-level protocol for how two peers can communicate. It includes handshake procedures and the means for transfering information such as blocks \& transactions.

%\section{Peer Strategy}\label{app:peers}

@@

$\langle 0_{256}, \mathtt{\tiny SHA3}(\mathtt{\tiny RLP}([])), 0_{160}, 0_{256}, \mathtt{\tiny SHA3}(\mathtt{\tiny RLP}([])), 2^{22}, 0, [], 42 \rangle$

@@

$\mathtt{\tiny SHA3}(\mathtt{\tiny RLP}([]))$ values refer to the hashes of the transaction and uncle lists in RLP, both empty.
